\section{Results}
\label{sec:results}

\subsection{Speckle Motion Detection}

The tapping, jumping and banging the door shut events in the experiments all produced a measurable deviation in the computed 1d signal. 
The piezo disc vibrations consistently and robustly produced a peak in the FFT at the frequency of the signal going into the piezo disc. 
Strong harmonics were also visible in the FFT when using the piezo disc.

Phase-shifted signals were observed across multiple photodiodes, indicating the presence of a moving speckle pattern. 
This phase information confirmed that the photodiode array could effectively visualize the dynamic speckle motion. 
The use of an IR LED further validated that the detected signals originated from laser speckle patterns and not from external light interference.
The results confirmed that the motion of speckle patterns was successfully detected using the discrete photodiode array. 

\subsection{Signal-to-Noise Ratio (SNR) Analysis}

The SNR analysis, as shown in Figure~\ref{fig:laser_snr}, demonstrated a positive correlation between the number of active lasers in the square array and the measurement quality. 
Incremental activation of the lasers resulted in an improvement in SNR.
The power spectral density analysis highlighted the 133 Hz vibration component of the piezo disc, 
with an R² value of 0.60 indicating a moderately strong relationship between the number of lasers and SNR enhancement.

Control experiments with all lasers turned off verified that the observed signals originated from the 
laser speckle patterns and not from other sources. 
These results support the hypothesis that the use of multiple lasers enhances the SNR, improving the sensitivity of the system.

\subsection{Circuit Performance}

The custom-designed PCB and amplifier circuit were validated using SPICE simulations and experimental measurements. 
The Bode plot in Figure~\ref{fig:bodeplot} demonstrated a flat frequency response with high gain, while 
the transient response shown in SPICE simulations confirmed system stability. 

\subsection{Impact of Experimental Parameters}

The experiments revealed several critical factors impacting the measurement results. 
The PCB required thorough cleaning with IPA and compressed air to eliminate flux residue, as any remaining contaminants introduced noise. 
Additionally, conducting experiments in a light-controlled environment was essential to prevent 
saturation of the opamp and ensure reliable data capture. 
The PCB had to be enclosed in a metal shield to limit the amount of incoming noise.
Dot projector alignment, facilitated by cameras, is critical for ensuring consistent speckle patterns and 
uniform distribution across the photodiode array.

\subsection{Limitations}
The opamp saturated in sunlight, rendering the signal irrecoverable in such conditions. Dot projectors cannot be 
effectively used as the reflected light intensity is too low.
Furthermore, the bandwidth of the system is limited to 1.5kHz due to the ADCs used.
